### 2021-09-29 papers/modeling-of-combined-lfr-csp-sco2-paper/content.tex
Finished conclusion, finalized comments, updated abstract

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having the most efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

@@

%Monnerie et al. (2011), in search of an alternative to the typical fossil fuel-based process, reports on combining nuclear and solar energy in the same plant to produce hydrogen \cite{monnerie_2011}.  Extraction and production of fuels using complimentary solar-nuclear systems is additionally studied in the Curtis 2015 thesis from Massachusetts Institute of Technology where cycle configuration, performance, and development of shale oil extraction from kerogen deposits is reported \cite{curtis_2015}. Utilizing complimentary solar-nuclear cycles for production of hydrogen or shale oil with economical feasibility of the system discussed, in contrast to a fucus on electrical generation and storage in a sCO$_2$ Brayton recompression cycle, is not within the scope of the presented research in this paper.

%Implementation of a combined solar and nuclear plant, modeled in the Wang et al. (2020) shows a single sCO$_2$ Brayton recompression cycle layout with an emphasis on a cycle design's performance to varying solar irradiance and demonstration of feasibility \cite{wang_2020}.  This single cycle configuration has a dissimilar higher-temperature operating salt, KCl-MgCl$_2$, as the heat transfer fluid in the CSP with the small modular lead-cooled fast reactor's main purpose as a preheater to the CSP heat addition instead of being utilized as an TES charging alternative. Presented in this paper are the effects on cycle and heat storage efficiency of alternative heat addition locations while having the LFR serve a dual purpose of electrical generation and a supplementary CSP TES charging technique. 
%This paper will provide an overview of contending recompression sCO$_2$ Brayton cycles with varied positioning of complimentary CSP and LFR heat additions in the cycle. Additionally the location of where heat is drawn from the sCO$_2$ Brayton cycles to be stored in thermal energy storage is studied and the results discussed.
\bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences). You could start by saying that it is prior work on the LFR-CSP-sCO2 concept. Then describe its cycle configuration with the high temperature salt. Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed. The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang - BW}

@@

%MW: I've fixed spelling in a few places. You can install a spell checker to highlight misspelled words. I use the "Code spell checker" extension.

@@

%Power calculations are initially done on ideal, reversible compressors or turbines then are scaled by the isentropic efficiencies to provide an estimate for a realizable component.\mw{this is kind of an awkward way to describe what's happening. I think most readers are familiar with isentropic efficiencies and this can be omitted.}

@@

%\mw{This is for a single flow stream. Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream? Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$. -BW}

@@

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simple counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

%\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}

@@

The CSP salt cycle uses 60\% sodium nitrate, NaNO$_3$, and 40\% potassium nitrate, KNO$_3$, 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to 720$^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at 560$^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilities: 390$^{\circ}$C, 410$^{\circ}$C, and 440$^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. While the hot TES is charging, the receiver and LFR are storing heat for later use when grid demand increases. The hot TES storage is not dispensing salt for use in the CSP cycle while charging.

The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use. Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle. Additionally, while the focus is on heat storage, and the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot TES.
%\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP? }

@@

\subsection{Standardization of Cycle Modeling}
%======================================================================================
%\mw{What do you mean by ``generalized?''-BW}

@@

\begin{specialtable}[H] 
    %[htbp]
    %\mw{Also changing the specialtable position to allow latex to better place tables.-BW}
    \caption{Standardized constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{L{0.5\linewidth}cc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pumps 1-3 & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 ($^{\circ}$C)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 ($^{\circ}$C)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 ($^{\circ}$C)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 28.8 (MPa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 950 (MW)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 750 (MW)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 40 ($^{\circ}$C)\\
    %Lead-Cooled Fast Reactor sCO$_{2}$ Low Temperature & $T_{4}$,$T_{1C}$,$T_{5A}$,$T_{4C}$ & 673.2 (K)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 595 ($^{\circ}$C)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726 (MPa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3 (MPa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

In addition to standardized parameters, all cycles have identical recompression sides. The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor. 
\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations. It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.-BW}
%\mw{components don't need to be capitalized -- they aren't proper nouns -BW}

Modeled cycles are summarized in Table \ref{tab-cycle_sum}.

@@

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}. 
%\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.}

@@

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The constrained study is calculated by setting the LFR inlet temperature to the design value of $400^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits. In addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency. The unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency. In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post. 
%%\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint}

@@

One drawback of having a two-cycle design, as seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components. Combining the two cycles into one would reduce redundancy and complexity. Heat addition from the CSP HX and LFR HX in parallel orientation is therefore studied in the C-1HTR1T-ON model. This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency. The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.

%%\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from}
%\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

The C2S is located around the turbine and LFR at state points 5 to 6 depending on the charging cycle configuration: pre, parallel, post or circulator. In the C-1HTR1T-ON cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are done on the model. The initial two studies have the low LFR temperature constrained to the value of $400^{\circ}$C with varied cold CSP TES temperature and maximized cycle efficiency. To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, is parametrically studied.
%\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
Two cold TES temperatures are tested with constrained LFR low temperature of $400^{\circ}$C: 
\begin{itemize}
    \item	$410^{\circ}$C: Lowest cold TES temperature possible due to the sCO$_2$ cold inlet constrained from the LFR to $400^{\circ}$C and the addition of $10^{\circ}$C approach temperature;
    \item	$440^{\circ}$C: Upper bound temperature on cold TES storage;
\end{itemize}

@@

In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C. The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX increasing dispatchability.
%%\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability -BW}

@@

Mixing two different temperature flows before the turbine in a Brayton cycle has a negative effect on cycle efficiency \mw{compared to...?}. To quantify the reduction in cycle efficiency, another cycle with no mixing prior to the turbine is desired. This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines. The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR. 
%\mw{The LFR doesn't recuperate heat. Clarify what you mean here. -BW} 
The cycle with heat addition from the CSP also contains two separate turbines, T2, while having a dedicated high temperature recuperator, HTR2. 
\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.} 
After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
%\bl{this is more about having a compromise option of intermediate complexity and efficiency}
\bl{also why this isnt really an addition turbine, it is using the turbines that power the compressors}

@@

The C2S heat exchanger is located around the turbine and LFR at 7A to 8A depending on the charging configuration: pre, post, parallel or circulator. Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint. The two constrained studies have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C. The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.  
%\bl{this is clearer than the previous one but bullets could still be useful}

@@

In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX. 
\mw{not a full sentence -BW}

@@

%\mw{write matter-of-factly, not in a hypothetical tense.-BW}

@@

%%\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}

@@

The values for the three non-charging cycle models with a focus on electrical generation, 2-cycle configuration composed of C-LFR-ON and C-CSP-ON, C-1HTR1T-ON, and C-2HTR3T-ON, are displayed in Table \ref{tab-noncharg}.

@@

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to 400$^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of 390$^{\circ}$C, 410$^{\circ}$C, or 440$^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.

@@

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%. The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}. Increasing the LFR sCO$_2$ inlet temperature above the design value of 400$^{\circ}$C is favorable from a cycle efficiency perspective, but reduces the LFR thermal power. This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power. In principle, dropping the LFR inlet temperature further, to as low as 340$^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed. When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by 15.1$^{\circ}$C to a value of 415.1$^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.

C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because C2S is turned off and therefore the two cycles are not tethered during non-charging configuration. Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of 390$^{\circ}$C and another with a higher value of 440$^{\circ}$C. A cold TES temperature of 410$^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the 390$^{\circ}$C and 440$^{\circ}$C calculated values. Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the 440$^{\circ}$C case gaining 0.35\%. The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of 390$^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.

>>>>

Recompression supercritical CO$_2$ Brayton cycles are promising cycle configurations offering higher efficiencies, compact design, and reduced turbomachinery cost while operating with non toxic working fluid. High efficiencies, in some simple recompression cycles reaching 50\% efficiency \cite{turchi_2013,wright_2009}, allows these cycles to be a competitive alternative to steam Rankine and air Brayton cycles over a range of temperatures.
\bl{Updated above as sCO2 can also be used for Coal - it is a cycle vs cycle argument rather than a heat source vs heat source argument -BW}
Various sCO$_2$ Brayton cycles have been modeled with the recompression cycle having efficiency advantages over other proposed cycle arrangements \cite{turchi_2013,ahn_2014,wang_2018}.  Due to the benefits of sCO$_2$ Brayton cycles, the United States Department of Energy is investigating these conversion cycles for use with heat sources including nuclear and solar \cite{doe_2012}. Multiple project funding opportunities are established with the National Energy Technology Laboratory offering 144 million dollar reward for demonstration and performance verification of a sCO$_2$ Brayton cycle \cite{netl_2016} and the Office of Energy Efficiency \& Renewable Energy offering 2.6 million dollar reward in their Brayton Energy project for a integrated CSP receiver, TES, and power block in one sCO$_2$ Brayton system \cite{seto_2015}. Utilizing complementary technologies, specifically solar concentrating power and lead-cooled fast reactors, can offset the drawbacks of each. Coupling these technologies into an interconnected cycle allows for consistent generation, independent of weather or time of day, and thermal storage for high dispatchability during high grid demand periods.

@@

\bl{I think the last citation merits its own paragraph and a little further discussion (1-2 more sentences). You could start by saying that it is prior work on the LFR-CSP-sCO2 concept. Then describe its cycle configuration with the high temperature salt. Then in the following sentence (the stuff you currnetly have highlighted) you can say that your work is investigating higher lead temperatures than Wang (because of Westinghouse LFR) and lower temperature salt (technology readiness) and this leads to very different cycle configurations and options than Wang, as will be discussed. The overall tone is that you work recognizes and builds on Wang, rather than needing to justify its existance despite Wang - BW}

@@

@@

\mw{this is kind of an awkward way to describe what's happening. I think most readers are familiar with isentropic efficiencies and this can be omitted.-BW}

@@

\mw{This is for a single flow stream. Why would there be $\dot{Q}_{in}$ and $\dot{Q}_{out}$ in a single flow stream? Also, the variable should be consistent with the figure, which would be $\dot{Q}_{HX}$. -BW}

@@

\end{paracol}
\begin{figure}[H] 
    \widefigure
    \includegraphics[width=10 cm]{Definitions/counter-flow-hx.pdf}
    \caption{Simplified counter-flow heat exchanger diagram. \label{counter-flow-hx}}
\end{figure}
\begin{paracol}{2}
\linenumbers
\switchcolumn

@@

\mw{Best practice is to allow figures to float. To do this, specify the location as [htb] ("here, top, or bottom"). I've done a search-replace for all figures to do this. -BW}

@@

The CSP salt cycle uses 60\% sodium nitrate, NaNO$_3$, and 40\% potassium nitrate, KNO$_3$, 'solar salt' as the heat transfer fluid. Solar salt stored in the hot TES can be dispatched on demand through the CSP HX when grid demand increases and held when grid demand is low. Current CSP salt cycles heat solar salt with receivers and store it in hot TES tanks at temperatures around 565$^{\circ}$C. Future CSP salt cycles are hypothesized to have bulk hot TES temperatures of up to $720^{\circ}$C, but due to high temperature limitations with the LFR outlet, the hot TES temperature is set at $560^{\circ}$C for all modeled cycles \cite{mehos2017concentrating}. The cold TES temperature takes on three different values according to cycle configuration capabilities: $390^{\circ}$C, $410^{\circ}$C, and $440^{\circ}$C. In addition to the lower hot TES temperature, current CSP salt cycles lack a secondary option for charging the hot TES \cite{hamilton2020dispatch}. The studied CSP salt cycle has two TES charging options: a receiver, which generates heat from a heliostat field, and C2S heat exchanger, which draws excess heat from the sCO$_2$ Brayton cycle. While the hot TES is charging, the receiver and LFR are storing heat for later use when grid demand increases. The hot TES storage is not dispensing salt for use in the CSP cycle while charging.

The C2S heat exchanger is active in the 'charging' cycle operating modes, when the focus is on heat storage for later use. Pump 1 is actively moving solar salt from cold TES to hot TES through the C2S heat exchanger extracting heat from the sCO$_2$ Brayton cycle. Additionally, while the focus is on heat storage, and the heliostat field is inputting heat, pump 2 is actively transporting solar salt through the receiver to be stored in the hot TES.
\mw{Is this necessarily true? Couldn't there be a condition where we'd like to dump energy from the LFR while simultaneously collecting from CSP?-BW}

@@

\subsection{Standardization of Cycle Modeling}
%======================================================================================
\mw{What do you mean by ``generalized?''-BW}

@@

\begin{specialtable}[H] 
    %[htbp]
    \caption{Standardized constant cycle parameters with definition, variable and set value. \label{tab-cycle-constants}}
    \begin{tabular}{L{0.5\linewidth}cc}
    \toprule
    \textbf{Parameter} & \textbf{Variable}	& \textbf{Design Point Value}\\
    \midrule
    \textit{Efficiencies}\\
    Main Compressor & $\eta_{MC}$		& 0.91 (-)\\
    Re-Compressor & $\eta_{RC}$		& 0.89 (-)\\
    Turbine & $\eta_{T}$		& 0.90 (-)\\
    Pumps 1-3 & $\eta_{P}$      & 0.90 (-)\\
    \midrule
    \textit{Approach Temperatures}\\
    Low Temperature Recuperator & $\delta_{LTR}$		& 10 ($^{\circ}$C)\\
    High Temperature Recuperator & $\delta_{HTR}$		& 10 ($^{\circ}$C)\\
    Concentrating Solar Power Heat Exchanger & $\delta_{CSPHX}$	& 10 ($^{\circ}$C)\\
    \midrule
    \textit{Pressures}\\
    Pressure Ratio & $PR$ & 3.27 (-)\\
    High Side Pressure & $P_{2A}$ & 28.8 (MPa)\\
    \midrule
    \textit{Heat Into System}\\
    Lead-Cooled Fast Reactor Heat Transfer & $\dot{Q}_{LFRHX}$ & 950 (MW)\\
    Concentrating Solar Power Heat Transfer & $\dot{Q}_{CSP}$ & 750 (MW)\\
    \midrule
    \textit{Temperature}\\
    Main Compressor Inlet & $T_{1A}$ & 40 ($^{\circ}$C)\\
    Lead-Cooled Fast Reactor sCO$_{2}$ High Temperature & $T_{5}$,$T_{2C}$,$T_{6A}$,$T_{5C}$ & 595 ($^{\circ}$C)\\
    \midrule
    \textit{Pumps}\\
    Pressure Rise Across Pump & $\Delta_{P}$ & 3.726 (MPa)\\
    Pump Low Side Pressure & $P_{S5-B}$ & 3 (MPa)\\ 
    \bottomrule
    \end{tabular}
\end{specialtable}

@@

In addition to standardized parameters, all cycles have identical recompression sides. The recompression side contains a precooler, low temperature recuperator, and two compressors; main compressor and recompressor. 
\mw{We need an overview here of our process for identifying which cycles will be modeled, as the discussion below gets a bit complicated with all of the different permutations. It might be helpful to have a model taxonomy that schematically shows how the different models are related to each other.-BW}
\mw{components don't need to be capitalized -- they aren't proper nouns -BW}
The modeled cycles are summarized in Table \ref{tab-cycle_sum}.

@@

The cycle that is using the LFR heat input in the two-cycle configuration is labeled as C-LFR-ON and the cycle diagram is illustrated in Figure \ref{c-lfr-on}. 
\mw{There are lots of little 1-2 sentence ``paragraphs'' that could be consolidated with some thought.-BW}

@@

Two separate sensitivity studies on the LFR inlet temperature are completed for C-LFR-ON. The constrained study is calculated by setting the LFR inlet temperature to the design value of $400^{\circ}$C, which is a requirement of the LFR primary circuit to maximize power output within material limits. In addition to the constrained studies, unconstrained studies are required to test the penalties that LFR inlet temperature has on efficiency. The unconstrained study is performed by gradually increasing the mass flow to the main compressor through a parametric study while maximizing cycle efficiency. In Figure \ref{c-lfr-on}, the location of the C2S heat exchanger while charging falls between state point 5 and 6 in any of the studied charging configurations: parallel, pre, circulator or post. 
\bl{flip the order of this para: constrained then unconstrained. State that the unconstrained is a 'sensitivty' case to determine the penalty of the constraint-BW}

@@

One drawback of having a two-cycle design, as seen in the C-LFR-ON and C-CSP-ON, is doubling the number of system components. Combining the two cycles into one would reduce redundancy, complexity, and cost. Heat addition from the CSP HX and LFR HX in parallel orientation is therefore studied in the C-1HTR1T-ON model. This model studies what impact mixing different temperature flows prior to the turbine has on cycle efficiency. The diagram for this cycle is illustrated in Figure \ref{c-1htr1t-on}.

\bl{be clear that Salt HX links back into the sCO2 cycle (e.g. parallel to 5-6) but is not shown to simplify the diagram. Otherwise people will wonder where it is coming from-BW}
\mw{After lots of tinkering, I've not solved how to get the figures to avoid spilling over the edge of the page. I think it's a problem with the MDPI template. The figures have a lot of whitespace between components and numbers, and you may need to try to compress some of them down to make them more compact.-BW}
\end{paracol}

@@

The C2S is located around the turbine and LFR at state points 5 to 6 depending on the charging cycle configuration: pre, parallel, post or circulator. In the C-1HTR1T-ON cycle, the LFR HX and CSP HX have identical inlet temperatures due to splitting the flow prior to their parallel orientation. Therefore, three sensitivity studies are done on the model. The initial two studies have the low LFR temperature constrained to the value of $400^{\circ}$C with varied cold CSP TES temperature and maximized cycle efficiency. To achieve a maximum cycle efficiency, the split fraction amount of flow to the main compressor, $y_{1}$, is parametrically studied.
\mw{State what variable(s) are manipulated in order to maximize cycle efficiency -BW} 
Two cold TES temperatures are tested with constrained LFR low temperature of $400^{\circ}$C: 
\begin{itemize}
    \item	$410^{\circ}$C: Lowest cold TES temperature possible due to the sCO$_2$ cold inlet constrained from the LFR to $400^{\circ}$C and the addition of $10^{\circ}$C approach temperature;
    \item	$440^{\circ}$C: Upper bound temperature on cold TES storage;
\end{itemize}

@@

In the third case the constraint on the LFR low temperature is removed, dropping the temperature of the LFR inlet to $380^{\circ}$C. The desired cold TES temperature of $390^{\circ}$C allows for a larger temperature drop across the CSP HX, increasing dispatchability.
\bl{I think I understand what you're talking about but the above para could spell out all the sensitivity cases a bit more clearly, perhaps as bullets. Asp you will want to explain the criteria that go into cold storage temp. Lower = more delta T = more dispatchability -BW}

@@

The identical inlet temperatures due to the parallel configuration makes the C-1HTR1T-ON cycle configuration restricted. Another single cycle configuration is desired to allow dissimilar inlet temperatures for the CSP HX and LFR HX while additionally testing the effect that mixing flows downstream from the HTR has on cycle efficiency. This cycle, C-2HTR3T-ON, can be seen in Figure \ref{c-2htr3t-on} and has two high temperature recuperators and three turbines. The LFR is powering one turbine, T1, and transferring unused heat to the flow entering LFR HX through a dedicated high temperature recuperator, HTR. The cycle with heat addition from the CSP also contains two separate turbines, diagrammatically shown as one turbine T2, while having a dedicated high temperature recuperator, HTR2. The two turbines displayed as T2 can be modeled as a singular turbine because their isentropic efficiencies are identical causing the inlet and outlet conditions of the turbines to be consistent with a singular turbine. Additionally, the power produced by the two turbines is proportional to mass flow rate, each receives a fraction of the mass flow rate therefore producing the same fraction of power. Summing these power fractions together yields the total power of a singular turbine in the same position. 
\mw{Need to explain how T2 is actually 2 separate turbines represented diagramatically as 1, and why we can model it this way.-BW} 
After the high temperature recuperators, the two flows are combined and sent to the LTR hot side. 
\bl{this is more about having a compromise option of intermediate complexity and efficiency}
\bl{also why this isnt really an addition turbine, it is using the turbines that power the compressors -BW}

@@

The C2S heat exchanger is located around the turbine and LFR at 7A to 8A depending on the charging configuration: pre, post, parallel or circulator. Three sensitivity studies are done on the C-2HTR3T-ON model -- two with the LFR low temperature constrained and one without this constraint. The two constrained studies, with an LFR temperature of $400^{\circ}$, have varied cold CSP TES temperature with the lowest temperature of $390^{\circ}$C and highest temperature of $440^{\circ}$C. The unconstrained low LFR inlet study is calculated at a cold CSP TES temperature of $390^{\circ}$C.

@@

In the heat storage efficiency equation, $\dot{Q}_{C2S}$ is the amount of heat transferred through C2S, and the addition of $\dot{Q}_{LFRHX}$ and $\dot{Q}_{CSPHX}$ is the total amount of heat input into the system from the LFR HX and CSP HX.

@@

@@

\bl{explain why you are considering this case (avoid losing useful energy in compressor and turbine inefficiencies)} \mw{agree with Ben. Additional motivation is needed -BW}

@@

The three non-charging cycle models have a focus on producing the highest positive alternator power to heat input, or cycle efficiency. The two-cycle configuration, composed of C-LFR-ON and C-CSP-ON, has independent recompression cycles with dedicated compressors, turbine, recuperators, and precooler for the LFR and CSP. C-1HTR1T-ON, with the heat additions in parallel, and C-2HTR3T, with dedicated HTR for both heat additions, are cycles which incorporate the CSP and LFR in the same cycle. The results from studies done on these cycles are displayed in Table \ref{tab-noncharg}.

@@

The calculated values reported in Table \ref{tab-noncharg} are component power, mass flow fractions, and counter-flow heat exchanger specifications. Columns labeled with '$C$' headers have the LFR sCO$_2$ low inlet temperature constrained to $400^{\circ}$C while those labeled with '$U$' are unconstrained and calculated based off of a parametric study on the MC mass flow fraction. Values listed in the Cold TES Temperature row are set to values of $390^{\circ}$C, $410^{\circ}$C, or $440^{\circ}$C to study the effects that cold TES temperature has on cycle efficiency and to accommodate certain characteristics of cycle configurations. Cycles with data entries labeled not applicable (N/A) do not contain the component listed and therefore do not have values associated with the component.

@@

The two-cycle configuration has the CSP and LFR operating in separate recompression cycles when the focus is on electrical generation, therefore these two cycles are analyzed individually. C-LFR-ON has the highest efficiency during unconstrained operation with a gain of 1.8\%. The unconstrained case allows for smaller temperature gradient across the LFR, an increase in recuperator effectiveness, and an increase in recuperator capacitance ratio, all of which reduce sources of irreversibility in the cycle \cite{klein_nellis_2011}. Increasing the LFR sCO$_2$ inlet temperature above the design value of $400^{\circ}$C is favorable from a cycle efficiency perspective, but reduces the LFR thermal power. This is because the LFR mass flow rate and outlet temperature are constrained by materials properties (to limit creep, corrosion and erosion), so a lower inlet temperature implies a lower thermal power. In principle, dropping the LFR inlet temperature further, to as low as $340^{\circ}$C (beyond which lead freezing becomes limiting), would further increase thermal power at the expense of cycle efficiency, so a trade-off is needed. When unconstrained, the sCO$_2$ inlet temperature to the LFR increases by $15.1^{\circ}$C to a value of $415.1^{\circ}$C, increasing LFR efficiency but demanding a larger, more idealized, LFR heat exchanger.

C-CSP-ON is not affected by constrained or unconstrained LFR sCO$_2$ inlet temperature because C2S is turned off and therefore the two cycles are not tethered during non-charging configuration. Two individual studies are conducted on the C-CSP-ON cycle cold TES temperature, one with a lower design value of $390^{\circ}$C and another with a higher value of $440^{\circ}$C. A cold TES temperature of $410^{\circ}$C is excluded since it can be presumed to have an efficiency intermediate to the $390^{\circ}$C and $440^{\circ}$C calculated values. Cold TES temperature is found to have a negligible effect on cycle efficiency between the two studied cases, with the $440^{\circ}$C case gaining 0.35\%. The component that has the largest change in values is the CSP HX with a large drop in capacitance ratio and UA value, therefore the lower temperature of $390^{\circ}$C for cold TES temperature is ideal increasing the performances of the heat exchanger.

Combining the two-cycle efficiencies using Equation \ref{eq-eta-2cycle} gives a more direct comparison to the single cycle configurations; C-1HTR1T and C-2HTR3T. Two combined efficiencies are calculated for the two-cycle configuration combination. The first has the highest efficiency, combining the unconstrained C-LFR-ON LFR low temperature and C-CSP-ON $440^{\circ}$C cold TES cases. This combined efficiency yields a value of 46.05\%. The second combined configuration has a lower efficiency with favorable LFR characteristics and solar salt mass flow rate. This combination has the constrained C-LFR-ON LFR low temperature and C-CSP-ON $390^{\circ}$C cold TES cases with a combined efficiency of 45.05\%. 
\bl{can you produce a combined efficiency which is total cycle electrical output/total heat input for C-LFR-ON + C-CSP-ON in combination-BW}
